A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
more fpp text

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate \citep{Morton:2011, Fressin:2013}, primarily due
to two major factors.  First, the superior precision of
the \kepler\ photometry enabled

>>>>

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
primarily due to two major factors.  First, the superior precision of
the \kepler\ photometry enables detection of secondary stellar
eclipses to a much lower level than ground-based surveys; and second,
the relatively small pixels and stable pointing of the
\kepler\ telescope has enabled the identification of many spatially
distinct blended eclipsing binaries by means of detailed pixel-level
analysis \citep{Bryson:2013}.
